The CMS Data Aggregation System

### 2010-05-04 doc/paper.tex
Update numbers
git-svn-id: svn+ssh://svn.cern.ch/reps/CMSDMWM/DAS/trunk@678 4525493e-7705-40b1-a816-d608a930855b

\begin{table*}[hbt]
\centering
\begin{tabular}{llllll}\hline
\hline
System & Format & Size & Records & Elapsed time & Elapsed time \\
& & & & no cached data & w/ cached data \\
\hline
DAS (DBS) & XML & 187MB & 368716 & 53 sec & 0.92 sec \\
DAS (PhEDEx) & XML & 164MB & 175884/170131 & 160 sec & 0.94 sec \\
DAS (aggregate) & JSON & 357MB & 374468 & 256 sec & 44.8 sec \\
\hline
\hline
\end{tabular}
\caption{Time required to fetch, parse and aggregate block information
from DBS and PhEDEx systems. In the case of PhEDEx
system we show total number of fetched records 175884 together with
number of records merged in DAS 170131. The total number of DAS records 
were calculated as number of aggregated records plus left overs,
the non-matched records from both systems.}
\label{DAS_benchmark}
\end{table*}

@@

The individual tests of DAS components (DBS and PhEDEx) shown roughly 
the same performance. Although the time of PhEDEx component was bigger 
due to longer retrieval and parsing time.
The time of PhEDEx component shown in Table \ref{DAS_benchmark} is divided 
among retrieval and parsing, $\sim$110 sec, and merging steps, $\sim$50 sec,
respectively. As shown in Table \ref{DAS_benchmark},
the time spent to access individual components (last column) was quite
reasonable, roughly 1 second for both systems. While final time to
get DAS records on disk was about 45 seconds. This was mostly due to I/O and
conversion operations between binary data format used by MongoDB, BSON, to DAS
data format, JSON.

Based on results of stress tests we measured that we can achieve throughput of
7000 docs/sec for insertion, 3400 docs/sec for aggregation and 8500 docs/sec for 
reading operations in DAS, which are suitable for our needs. Since all 
operations were performed on a single CPU a further improvements are expected. 
Also, a necessary tuning can be done by using C++ driver instead of python one.

>>>>

\begin{table*}[hbt]
\centering
\begin{tabular}{lllll}\hline
\hline
System & Format & Records & Elapsed time & Elapsed time \\
& & & no cached data & w/ cached data \\
\hline
DAS (DBS) & XML & 382396 & 63 sec & 0.98 sec \\
DAS (PhEDEx) & XML & 186145/180439 & 164 sec & 0.98 sec \\
DAS (aggregate) & JSON & 388108 & 234 sec & 2.05/50.7 sec \\
\hline
\hline
\end{tabular}
\caption{Time required to fetch, parse and aggregate block information
from DBS and PhEDEx systems. In the case of PhEDEx
system we show total number of fetched records 186145 together with
number of records merged in DAS 180439. The total number of DAS records 
were calculated as number of aggregated records plus left overs,
the non-matched records from both systems. The look-up time is presented in
last column, where for DAS it shows as query look-up time (2.05 sec) 
and time to get all records to disk (50.7 sec).}
\label{DAS_benchmark}
\end{table*}

@@

The individual tests of DAS components (DBS and PhEDEx) shown roughly 
the same performance. Although the time of PhEDEx component was bigger 
due to longer retrieval and parsing time.
The time of PhEDEx component shown in Table \ref{DAS_benchmark} is divided 
among retrieval and parsing, $\sim$110 sec, and merging steps, $\sim$50 sec,
respectively. As shown in Table \ref{DAS_benchmark},
the look-up time spent to access individual components (last column) was quite
reasonable, roughly 1 second for both systems. While final time to
get DAS records on disk was about 50 seconds. This was mostly due to I/O and
conversion operations between binary data format used by MongoDB, BSON, to DAS
data format, JSON.

Based on results of stress tests we measured that we can achieve throughput of
$\sim$6000 docs/sec for insertion, $\sim$1100 docs/sec for aggregation and 
$\sim$7600 docs/sec for 
reading operations in DAS, which are suitable for our needs. Since all 
operations were performed on a single CPU a further improvements are expected. 
Also, a necessary tuning can be done by using C++ driver instead of python one.
